IML Term project paper

### 2022-12-11 paper.rmd
Update paper.rmd
Lisätty taulu, joka tiivistä tulokset

@@

With our observed best-performing models being the logistic regression model, the Lasso regression model and the linear discriminant analysis. Out of these models, we eventually chose to use the logistic regresison model. The Lasso model was our best-performing model, but we eventually chose not to use it for practical reasons related to computational heaviness in calculating the multi-class model. Mainly, the amount of information we could gain through calculations in R without R crashing was relatively limited, to the degree that we couldn't always even calculate the cross-validated best choice for the tuning parameter.

@@

@@

## Classifier performance (numerical)

>>>>

## Classifier performances (numerical)

In order to reduce knitting time for the file, we will in this preliminary report instead of expressing the full R code to calculate the values, simply report the results we received and instead return the full R code only with the final report. The results for the two-class models in terms of loo-cross-validated accuracy and perplexity are:
\begin{table}
\begin{tabular}{|r|cc|}
\hline
Model type & loo-cv accuracy & loo-cv perplexity\\
\hline
Dummy model & 0 & 2.01\\
Logistic regression & 0.89 & 1.30\\
Naive Bayes & 0.81 & 152.85\\
LDA & 0.89 & 1.33\\
QDA & 0.85 & 6.34\\
SVM & 0.88 & 1.34\\
Lasso & 0.89 & 1.29\\
Random Forest & 0.89 & 1.35\\

\end{tabular}
\end{table}

@@

With our observed best-performing models being the logistic regression model, the random forest model, the Lasso regression model and the linear discriminant analysis. Out of these models, we eventually chose to use the logistic regresison model. The Lasso model was our best-performing model, but we eventually chose not to use it for practical reasons related to computational heaviness in calculating the multi-class model. Mainly, the amount of information we could gain through calculations in R without R crashing was relatively limited, to the degree that we couldn't always even calculate the cross-validated best choice for the tuning parameter.

@@

We made the decision based on preliminary results, and though decision trees would represent an equally viable solution, we calculated those results only later on, and by that point had already calculated the results for the logistic regression model. However, for the final report we might consider transitioning to the decision tree model.

@@
